---
title: "Comprehensive Malaria Analysis Deterministic vs Stochastic Optimization"
subtitle: "Extended Analysis with Multiple Scenarios, Models, and Metrics"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
    theme: flatly
    highlight: tango
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 14,
  fig.height = 10,
  dpi = 300
)
```

# Setup and Libraries

```{r load-libraries}
# Load required libraries with error handling
required_packages <- c("tidyverse", "tidymodels", "themis", "tictoc", 
                      "parallel", "doFuture", "finetune", "GA", 
                      "patchwork", "glmnet", "xgboost", "nnet", 
                      "kernlab", "kknn", "ranger", "yardstick", "Matrix")

# Function to install and load packages
load_package <- function(pkg) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg, dependencies = TRUE)
    library(pkg, character.only = TRUE)
  }
}

# Load all packages
for (pkg in required_packages) {
  tryCatch({
    load_package(pkg)
    cat("Loaded:", pkg, "\n")
  }, error = function(e) {
    cat("Warning: Could not load package", pkg, ":", e$message, "\n")
  })
}

# Setup parallel processing
tryCatch({
  registerDoFuture()
  plan(multisession, workers = min(3, parallel::detectCores() - 1))
  cat("parallel processing configured with", min(3, parallel::detectCores() - 1), "workers\n")
}, error = function(e) {
  cat("Parallel processing setup failed, continuing sequentially\n")
})

# Set global options
options(tidymodels.quiet = TRUE)
set.seed(123)  # Global seed for reproducibility
```

```{r}
# Enhanced Data Generation with Multiple Scenarios
# Function to load and prepare external CSV data
load_external_data <- function() {
  tryCatch({
    if (file.exists("Malaria-Data.csv")) {
      external_data <- read_csv("Malaria-Data.csv", show_col_types = FALSE)
      cat("Loaded external dataset: Malaria-Data.csv\n")
      cat("Dimensions:", nrow(external_data), "×", ncol(external_data), "\n")
      
      # Print column names to help with target identification
      cat("Column names:", paste(names(external_data), collapse = ", "), "\n")
      
      # Standardize the target variable name and ensure factor levels
      if ("severe_maleria" %in% names(external_data)) {
        external_data$severe_maleria <- factor(external_data$severe_maleria, 
                                             levels = c(0, 1), 
                                             labels = c("Not_severe", "Severe"))
        cat("  - Found 'severe_maleria' column\n")
      } else if (any(grepl("severe|target|class|outcome|label", names(external_data), ignore.case = TRUE))) {
        target_col <- names(external_data)[grepl("severe|target|class|outcome|label", names(external_data), ignore.case = TRUE)][1]
        names(external_data)[names(external_data) == target_col] <- "severe_maleria"
        external_data$severe_maleria <- factor(external_data$severe_maleria, 
                                             levels = c(0, 1), 
                                             labels = c("Not_severe", "Severe"))
        cat("  - Renamed target column '", target_col, "' to 'severe_maleria'\n")
      } else {
        # If no clear target column found, check for binary columns
        binary_cols <- sapply(external_data, function(x) {
          is.numeric(x) && all(x %in% c(0, 1, NA))
        })
        
        if (any(binary_cols)) {
          target_col <- names(external_data)[binary_cols][1]
          names(external_data)[names(external_data) == target_col] <- "severe_maleria"
          external_data$severe_maleria <- factor(external_data$severe_maleria, 
                                               levels = c(0, 1), 
                                               labels = c("Not_severe", "Severe"))
          cat("  - Used binary column '", target_col, "' as target variable\n")
        } else {
          stop("Could not identify target variable. Please ensure your CSV has a column with 0/1 values for malaria severity.")
        }
      }
      
      # Remove any non-predictive columns (IDs, etc.)
      id_cols <- grep("id|ID|index|Index", names(external_data), ignore.case = TRUE)
      if (length(id_cols) > 0) {
        external_data <- external_data[, -id_cols]
        cat("Removed ID columns\n")
      }
      
      # Ensure all predictors are numeric
      predictor_cols <- names(external_data)[names(external_data) != "severe_maleria"]
      for (col in predictor_cols) {
        if (!is.numeric(external_data[[col]])) {
          external_data[[col]] <- as.numeric(as.factor(external_data[[col]]))
          cat("  - Converted", col, "to numeric\n")
        }
      }
      
      # Check for and handle missing values
      missing_count <- sum(is.na(external_data))
      if (missing_count > 0) {
        cat("Found", missing_count, "missing values\n")
        # Simple imputation with median for numeric variables
        for (col in predictor_cols) {
          if (any(is.na(external_data[[col]]))) {
            median_val <- median(external_data[[col]], na.rm = TRUE)
            external_data[[col]][is.na(external_data[[col]])] <- median_val
            cat("    - Imputed", col, "with median value:", round(median_val, 3), "\n")
          }
        }
      }
      
      if ("severe_maleria" %in% names(external_data)) {
        severe_count <- sum(external_data$severe_maleria == "Severe", na.rm = TRUE)
        total_count <- nrow(external_data)
        cat("Target distribution: Severe =", severe_count, "/", total_count, 
            "(", round(100 * severe_count / total_count, 1), "%)\n")
        cat("Features available:", length(predictor_cols), "\n")
        cat("Feature names:", paste(predictor_cols, collapse = ", "), "\n")
      }
      
      return(external_data)
    } else {
      cat("external dataset 'Malaria-Data.csv' not found, skipping\n")
      return(NULL)
    }
  }, error = function(e) {
    cat("Error loading external dataset:", e$message, "\n")
    return(NULL)
  })
}

generate_malaria_data <- function(n_samples = 1000, scenario = "simple_linear") {
  set.seed(123)
  
  # Define comprehensive scenario parameters
  scenarios <- list(
    simple_linear = list(
      noise = 0.1,
      correlation = 0.05,
      coef = c(1.5, 1.2, 0.8, 1.0, 0.9, -1.3, -1.1, 0.7, 0.6, 0.8, 0.5, -0.4),
      nonlinear = FALSE,
      description = "Simple linear relationships with low noise"
    ),
    
    complex_nonlinear = list(
      noise = 0.2,
      correlation = 0.3,
      coef = c(1.2, -0.8, 0.6, 0.9, -1.1, 0.7, -0.5, 0.4, 0.3, -0.6, 0.2, -0.3),
      nonlinear = TRUE,
      interaction_strength = 0.5,
      description = "Complex nonlinear with moderate interactions"
    ),
    
    high_noise = list(
      noise = 0.5,
      correlation = 0.4,
      coef = c(0.8, -0.6, 0.4, 0.7, -0.5, 0.3, -0.4, 0.2, 0.1, -0.3, 0.15, -0.2),
      nonlinear = TRUE,
      interaction_strength = 0.3,
      description = "High noise scenario with weak signals"
    ),
    
    highly_complex_nonlinear = list(
      noise = 0.3,
      correlation = 0.5,
      coef = c(1.0, -1.2, 0.9, -0.7, 1.1, -0.8, 0.6, -0.4, 0.5, -0.9, 0.3, -0.6),
      nonlinear = TRUE,
      interaction_strength = 0.8,
      polynomial_terms = TRUE,
      description = "Highly complex with polynomial terms and strong interactions"
    )
  )
  
  params <- scenarios[[scenario]]
  n_features <- length(params$coef)
  
  cat("Generating", scenario, "data:", params$description, "\n")
  
  # Generate features with correlation structure
  if (params$correlation > 0) {
    cor_matrix <- matrix(params$correlation, nrow = n_features, ncol = n_features)
    diag(cor_matrix) <- 1
    
    # Add some random variation to correlation
    for (i in 1:n_features) {
      for (j in 1:n_features) {
        if (i != j) {
          cor_matrix[i, j] <- cor_matrix[i, j] * runif(1, 0.5, 1.5)
        }
      }
    }
    
    # Ensure positive definite
    cor_matrix <- as.matrix(Matrix::nearPD(cor_matrix)$mat)
    L <- chol(cor_matrix)
    Z <- matrix(rnorm(n_samples * n_features), nrow = n_samples)
    X <- Z %*% L
  } else {
    X <- matrix(rnorm(n_samples * n_features), ncol = n_features)
  }
  
  # Generate outcome with complexity
  linear_pred <- X %*% params$coef
  
  # Add nonlinear terms if specified
  if (params$nonlinear) {
    # Add polynomial terms
    if (!is.null(params$polynomial_terms) && params$polynomial_terms) {
      poly_terms <- X[, 1:3]^2 * c(0.3, -0.2, 0.4)
      linear_pred <- linear_pred + rowSums(poly_terms)
    }
    
    # Add interaction terms
    if (!is.null(params$interaction_strength)) {
      interaction1 <- X[, 1] * X[, 2] * params$interaction_strength
      interaction2 <- X[, 3] * X[, 4] * params$interaction_strength * 0.8
      interaction3 <- sin(X[, 5]) * params$interaction_strength * 0.6
      linear_pred <- linear_pred + interaction1 + interaction2 + interaction3
    }
  }
  
  # Add noise and convert to probabilities
  linear_pred <- linear_pred + rnorm(n_samples, 0, params$noise)
  prob_severe <- plogis(linear_pred)
  severe_malaria <- rbinom(n_samples, 1, prob_severe)
  
  # Create data frame
  feature_names <- c("fever", "vomiting", "fatigue", "headache", "nausea", 
                    "loss_appetite", "abdominal_pain", "joint_pain", 
                    "muscle_aches", "chills", "sweating", "cough")
  
  data <- data.frame(X)
  names(data) <- feature_names
  data$severe_maleria <- factor(severe_malaria, levels = c(0, 1), 
                               labels = c("Not_severe", "Severe"))
  
  # Print data characteristics
  cat("  - Severe cases:", sum(severe_malaria), "/", n_samples, 
      "(", round(100 * mean(severe_malaria), 1), "%)\n")
  
  return(data)
}

# Generate all datasets
cat("Generating synthetic datasets...\n")
simple_linear <- generate_malaria_data(1000, "simple_linear")
complex_nonlinear <- generate_malaria_data(1000, "complex_nonlinear") 
high_noise <- generate_malaria_data(1000, "high_noise")
highly_complex <- generate_malaria_data(1000, "highly_complex_nonlinear")

# Load external data
external_data <- load_external_data()

# Combine all datasets
all_datasets <- list(
  "Simple Linear" = simple_linear,
  "Complex Nonlinear" = complex_nonlinear,
  "High Noise" = high_noise,
  "Highly Complex Nonlinear" = highly_complex
)

if (!is.null(external_data)) {
  all_datasets[["Real Malaria Dataset"]] <- external_data
}

cat("\nTotal datasets prepared:", length(all_datasets), "\n")
```


# Comprehensive Model Configuration

```{r model-configuration}
get_comprehensive_models <- function(train_data) {
  n_features <- ncol(train_data) - 1
  n_samples <- nrow(train_data)
  
  cat("Configuring models for", n_features, "features and", n_samples, "samples\n")
  
  models <- list(
    # Logistic Regression
    logreg = list(
      name = "Logistic Regression",
      model = logistic_reg(penalty = tune(), mixture = tune()) %>% 
        set_engine("glmnet") %>% 
        set_mode("classification"),
      recipe = recipe(severe_maleria ~ ., data = train_data) %>%
        step_normalize(all_predictors()) %>%
        step_zv(all_predictors()) %>%
        step_corr(all_predictors(), threshold = 0.95),
      params = parameters(
        penalty(range = c(-4, 1), trans = log10_trans()),
        mixture(range = c(0, 1))
      )
    ),
    
    # Random Forest
    rf = list(
      name = "Random Forest",
      model = rand_forest(
        mtry = tune(), 
        trees = tune(), 
        min_n = tune()
      ) %>% 
        set_engine("ranger", importance = "impurity") %>% 
        set_mode("classification"),
      recipe = recipe(severe_maleria ~ ., data = train_data) %>%
        step_zv(all_predictors()),
      params = parameters(
        mtry(range = c(2L, max(2L, n_features))),
        trees(range = c(100L, 500L)),
        min_n(range = c(2L, 20L))
      )
    ),
    
    # Support Vector Machine
    svm = list(
      name = "Support Vector Machine",
      model = svm_rbf(cost = tune(), rbf_sigma = tune()) %>% 
        set_engine("kernlab") %>% 
        set_mode("classification"),
      recipe = recipe(severe_maleria ~ ., data = train_data) %>%
        step_normalize(all_predictors()) %>%
        step_zv(all_predictors()) %>%
        step_corr(all_predictors(), threshold = 0.95),
      params = parameters(
        cost(range = c(-2, 2), trans = log10_trans()),
        rbf_sigma(range = c(-4, -1), trans = log10_trans())
      )
    ),
    
    # Neural Network
    nnet = list(
      name = "Neural Network",
      model = mlp(hidden_units = tune(), penalty = tune(), epochs = tune()) %>% 
        set_engine("nnet", MaxNWts = 10000, trace = FALSE) %>% 
        set_mode("classification"),
      recipe = recipe(severe_maleria ~ ., data = train_data) %>%
        step_normalize(all_predictors()) %>%
        step_zv(all_predictors()) %>%
        step_corr(all_predictors(), threshold = 0.95),
      params = parameters(
        hidden_units(range = c(5L, 20L)),
        penalty(range = c(-4, -1), trans = log10_trans()),
        epochs(range = c(50L, 200L))
      )
    ),
    
    # XGBoost
    xgb = list(
      name = "XGBoost",
      model = boost_tree(
        trees = tune(),
        tree_depth = tune(),
        learn_rate = tune(),
        min_n = tune()
      ) %>% 
        set_engine("xgboost", verbosity = 0) %>% 
        set_mode("classification"),
      recipe = recipe(severe_maleria ~ ., data = train_data) %>%
        step_zv(all_predictors()),
      params = parameters(
        trees(range = c(50L, 300L)),
        tree_depth(range = c(3L, 8L)),
        learn_rate(range = c(-2, -0.5), trans = log10_trans()),
        min_n(range = c(2L, 10L))
      )
    ),
    
    # K-Nearest Neighbors
    knn = list(
      name = "K-Nearest Neighbors",
      model = nearest_neighbor(neighbors = tune(), weight_func = tune()) %>% 
        set_engine("kknn") %>% 
        set_mode("classification"),
      recipe = recipe(severe_maleria ~ ., data = train_data) %>%
        step_normalize(all_predictors()) %>%
        step_zv(all_predictors()) %>%
        step_corr(all_predictors(), threshold = 0.95),
      params = parameters(
        neighbors(range = c(3L, min(30L, n_samples %/% 5))),
        weight_func(values = c("rectangular", "triangular", "gaussian"))
      )
    )
  )
  
  cat("Configured", length(models), "models successfully\n")
  return(models)
}
```

# Control Functions and Tuning Methods

```{r control-functions}
# Ensure all control functions exist
if (!exists("control_random") || is.null(control_random)) {
  control_random <- function(verbose = FALSE, save_pred = FALSE, ...) {
    control_grid(verbose = verbose, save_pred = save_pred, ...)
  }
}

# Enhanced random search
tune_random_enhanced <- function(object, resamples, param_info = NULL, size = 25, 
                                metrics = NULL, control = control_grid()) {
  if (is.null(metrics)) {
    metrics <- metric_set(roc_auc, f_meas, accuracy, precision, recall, specificity)
  }
  
  grid <- param_info %>% grid_random(size = size)
  
  result <- tune_grid(
    object = object,
    resamples = resamples,
    grid = grid,
    metrics = metrics,
    control = control
  )
  
  return(result)
}

# Enhanced genetic algorithm
genetic_algorithm_tune <- function(workflow, resamples, param_info, 
                                  pop_size = 10, max_iter = 15, verbose = FALSE) {
  
  cat("    GA Parameters: pop_size =", pop_size, ", max_iter =", max_iter, "\n")
  
  best_fitness <- 0
  best_params <- NULL
  generation_results <- list()
  
  for (iter in 1:max_iter) {
    if (verbose) cat("Generation", iter, "of", max_iter, "\n")
    
    # Generate population
    population <- param_info %>% grid_random(size = pop_size)
    
    # Evaluate each individual
    for (ind in 1:nrow(population)) {
      tryCatch({
        individual <- as.list(population[ind, ])
        final_wf <- finalize_workflow(workflow, individual)
        
        cv_results <- fit_resamples(
          final_wf,
          resamples = resamples,
          metrics = metric_set(f_meas, roc_auc),
          control = control_resamples(save_pred = FALSE, verbose = FALSE)
        )
        
        fitness_f1 <- collect_metrics(cv_results) %>%
          filter(.metric == "f_meas") %>%
          pull(mean)
        
        fitness_auc <- collect_metrics(cv_results) %>%
          filter(.metric == "roc_auc") %>%
          pull(mean)
        
        # Combined fitness (weighted)
        fitness <- ifelse(length(fitness_f1) > 0 && length(fitness_auc) > 0,
                         0.7 * fitness_f1 + 0.3 * fitness_auc,
                         0)
        
        if (fitness > best_fitness) {
          best_fitness <- fitness
          best_params <- individual
        }
        
      }, error = function(e) {
        # Skip failed individuals
      })
    }
  }
  
  return(list(
    best_params = best_params,
    best_fitness = best_fitness,
    converged = !is.null(best_params)
  ))
}
```

# Comprehensive Metrics Setup with Efficiency and Stability Tracking

```{r metrics-setup}
# Define comprehensive metric set
comprehensive_metrics <- metric_set(
  accuracy,      # Overall accuracy
  f_meas,        # F1-score
  precision,     # Precision
  recall,        # Sensitivity/Recall
  specificity,   # Specificity
  roc_auc,       # ROC AUC
  pr_auc,        # Precision-Recall AUC
  bal_accuracy,  # Balanced Accuracy
  kap,           # Cohen's Kappa
  mcc            # Matthews Correlation Coefficient
)

# Global variables for tracking efficiency metrics
evaluation_counter <- list()
time_tracker <- list()

# Function to track evaluations
track_evaluation <- function(experiment_id) {
  if (!experiment_id %in% names(evaluation_counter)) {
    evaluation_counter[[experiment_id]] <<- 0
  }
  evaluation_counter[[experiment_id]] <<- evaluation_counter[[experiment_id]] + 1
  return(evaluation_counter[[experiment_id]])
}

# Function to get evaluation count
get_evaluation_count <- function(experiment_id) {
  return(ifelse(experiment_id %in% names(evaluation_counter), 
                evaluation_counter[[experiment_id]], 0))
}

# Function to reset counters
reset_counters <- function() {
  evaluation_counter <<- list()
  time_tracker <<- list()
}

# Function to calculate all metrics manually (backup)
calculate_comprehensive_metrics <- function(truth, estimate, prob_severe) {
  
  # Create confusion matrix components
  tp <- sum(truth == "Severe" & estimate == "Severe")
  tn <- sum(truth == "Not_severe" & estimate == "Not_severe")
  fp <- sum(truth == "Not_severe" & estimate == "Severe")
  fn <- sum(truth == "Severe" & estimate == "Not_severe")
  
  # Basic metrics
  accuracy <- (tp + tn) / (tp + tn + fp + fn)
  precision <- ifelse((tp + fp) == 0, 0, tp / (tp + fp))
  recall <- ifelse((tp + fn) == 0, 0, tp / (tp + fn))  # Sensitivity
  specificity <- ifelse((tn + fp) == 0, 0, tn / (tn + fp))
  f1_score <- ifelse((precision + recall) == 0, 0, 2 * precision * recall / (precision + recall))
  
  # Balanced accuracy
  balanced_acc <- (recall + specificity) / 2
  
  # Matthews Correlation Coefficient
  mcc_num <- (tp * tn - fp * fn)
  mcc_den <- sqrt((tp + fp) * (tp + fn) * (tn + fp) * (tn + fn))
  mcc <- ifelse(mcc_den == 0, 0, mcc_num / mcc_den)
  
  # Cohen's Kappa
  po <- accuracy
  pe <- ((tp + fp) * (tp + fn) + (tn + fp) * (tn + fn)) / ((tp + tn + fp + fn)^2)
  kappa <- ifelse(pe == 1, 0, (po - pe) / (1 - pe))
  
  roc_auc_val <- NA
  tryCatch({
    roc_auc_val <- yardstick::roc_auc_vec(truth, prob_severe, event_level = "second")
  }, error = function(e) {
    roc_auc_val <<- NA
  })
  
  return(list(
    accuracy = accuracy,
    f1_score = f1_score,
    precision = precision,
    recall = recall,
    specificity = specificity,
    balanced_accuracy = balanced_acc,
    mcc = mcc,
    kappa = kappa,
    roc_auc = roc_auc_val,
    confusion_matrix = list(tp = tp, tn = tn, fp = fp, fn = fn)
  ))
}

# Function to run multiple stability runs for stochastic methods
run_stability_analysis <- function(workflow, resamples, param_info, opt_method, n_runs = 3) {
  
  results <- list()
  
  for (run in 1:n_runs) {
    set.seed(123 + run * 100)  # Different seed for each run
    
    tryCatch({
      if (opt_method == "random") {
        result <- tune_random_enhanced(
          workflow, resamples = resamples, param_info = param_info,
          size = 15, metrics = metric_set(f_meas, accuracy, roc_auc),
          control = control_grid(verbose = FALSE, save_pred = FALSE)
        )
      } else if (opt_method == "genetic") {
        ga_result <- genetic_algorithm_tune(
          workflow, resamples, param_info, pop_size = 8, max_iter = 10
        )
        if (ga_result$converged) {
          # Convert GA result to standard format
          best_params <- ga_result$best_params
          final_wf <- finalize_workflow(workflow, best_params)
          result <- fit_resamples(
            final_wf, resamples = resamples, metrics = metric_set(f_meas, accuracy, roc_auc),
            control = control_resamples(save_pred = FALSE, verbose = FALSE)
          )
        } else {
          result <- NULL
        }
      } else {
        result <- NULL
      }
      
      if (!is.null(result)) {
        best_result <- select_best(result, metric = "f_meas")
        cv_metrics <- collect_metrics(result) %>%
          filter(.config == best_result$.config)
        
        f1_score <- cv_metrics %>% filter(.metric == "f_meas") %>% pull(mean)
        accuracy <- cv_metrics %>% filter(.metric == "accuracy") %>% pull(mean)
        roc_auc <- cv_metrics %>% filter(.metric == "roc_auc") %>% pull(mean)
        
        results[[run]] <- list(
          f1_score = ifelse(length(f1_score) > 0, f1_score, NA),
          accuracy = ifelse(length(accuracy) > 0, accuracy, NA),
          roc_auc = ifelse(length(roc_auc) > 0, roc_auc, NA)
        )
      }
    }, error = function(e) {
      results[[run]] <- list(f1_score = NA, accuracy = NA, roc_auc = NA)
    })
  }
  
  # Calculate stability metrics
  f1_scores <- sapply(results, function(x) x$f1_score)
  f1_scores <- f1_scores[!is.na(f1_scores)]
  
  if (length(f1_scores) > 1) {
    return(list(
      mean_f1 = mean(f1_scores),
      sd_f1 = sd(f1_scores),
      cv_f1 = sd(f1_scores) / mean(f1_scores),
      min_f1 = min(f1_scores),
      max_f1 = max(f1_scores),
      n_successful_runs = length(f1_scores)
    ))
  } else {
    return(list(
      mean_f1 = ifelse(length(f1_scores) == 1, f1_scores[1], NA),
      sd_f1 = NA,
      cv_f1 = NA,
      min_f1 = ifelse(length(f1_scores) == 1, f1_scores[1], NA),
      max_f1 = ifelse(length(f1_scores) == 1, f1_scores[1], NA),
      n_successful_runs = length(f1_scores)
    ))
  }
}
```

# Main Analysis Function with Enhanced Tracking

```{r main-analysis}
run_comprehensive_analysis <- function(dataset, dataset_name) {
  cat("\n", rep("=", 80), "\n")
  cat("Analyzing:", dataset_name, "\n")
  cat(rep("=", 80), "\n")
  
  # Reset counters for this dataset
  reset_counters()
  
  # Data splitting with stratification
  set.seed(700)
  data_split <- initial_split(dataset, prop = 0.75, strata = severe_maleria)
  train_data <- training(data_split)
  test_data <- testing(data_split)
  
  # Create cross-validation folds - CHANGED TO 10-FOLD REPEATED 5 TIMES
  cv_folds <- vfold_cv(train_data, v = 10, repeats = 5, strata = severe_maleria)
  
  # Get model configurations
  models <- get_comprehensive_models(train_data)
  
  cat("Dataset info: n =", nrow(dataset), ", features =", ncol(dataset)-1, "\n")
  cat("Models to test:", length(models), "\n")
  cat("Cross-validation: 10-fold repeated 5 times (50 total folds)\n")
  cat("Target distribution - Severe:", sum(dataset$severe_maleria == "Severe"), 
      "/", nrow(dataset), "(", round(100 * mean(dataset$severe_maleria == "Severe"), 1), "%)\n")
  
  # Define optimization methods
  opt_methods <- list(
    # Deterministic methods
    bayesian = list(name = "Bayesian Optimization", type = "Deterministic"),
    grid = list(name = "Grid Search", type = "Deterministic"),
    
    # Stochastic methods  
    random = list(name = "Random Search", type = "Stochastic"),
    genetic = list(name = "Genetic Algorithm", type = "Stochastic"),
    hyperband = list(name = "Hyperband Racing", type = "Stochastic")
  )
  
  # Storage for results
  all_results <- list()
  total_experiments <- length(models) * length(opt_methods)
  current_exp <- 0
  
  # Run experiments
  for (model_name in names(models)) {
    model_config <- models[[model_name]]
    
    for (opt_name in names(opt_methods)) {
      current_exp <- current_exp + 1
      opt_config <- opt_methods[[opt_name]]
      experiment_id <- paste(dataset_name, model_name, opt_name, sep = "_")
      
      cat("\n[", current_exp, "/", total_experiments, "] Testing:", 
          model_config$name, "with", opt_config$name, "\n")
      
      # Create workflow
      wf <- workflow() %>%
        add_recipe(model_config$recipe) %>%
        add_model(model_config$model)
      
      # Time the optimization
      start_time <- Sys.time()
      
      # Run optimization with evaluation tracking
      opt_result <- NULL
      best_params <- NULL
      cv_metrics <- NULL
      n_evaluations <- 0
      
      tryCatch({
        if (opt_name == "bayesian") {
          n_evaluations <- 8 + 12  # initial + iter
          opt_result <- tune_bayes(
            wf, resamples = cv_folds, param_info = model_config$params,
            initial = 8, iter = 12, metrics = comprehensive_metrics,
            control = control_bayes(verbose = FALSE, save_pred = FALSE, no_improve = 8)
          )
        } else if (opt_name == "grid") {
          n_evaluations <- 20
          opt_result <- tune_grid(
            wf, resamples = cv_folds, param_info = model_config$params,
            grid = 20, metrics = comprehensive_metrics,
            control = control_grid(verbose = FALSE, save_pred = FALSE)
          )
        } else if (opt_name == "random") {
          n_evaluations <- 25
          opt_result <- tune_random_enhanced(
            wf, resamples = cv_folds, param_info = model_config$params,
            size = 25, metrics = comprehensive_metrics,
            control = control_grid(verbose = FALSE, save_pred = FALSE)
          )
        } else if (opt_name == "genetic") {
          n_evaluations <- 12 * 15  # pop_size * max_iter
          ga_result <- genetic_algorithm_tune(
            wf, cv_folds, model_config$params, pop_size = 12, max_iter = 15
          )
          if (ga_result$converged) {
            best_params <- ga_result$best_params
            # Get CV metrics for best params
            final_wf <- finalize_workflow(wf, best_params)
            cv_results <- fit_resamples(
              final_wf, resamples = cv_folds, metrics = comprehensive_metrics,
              control = control_resamples(save_pred = FALSE, verbose = FALSE)
            )
            cv_metrics <- collect_metrics(cv_results)
          }
        } else if (opt_name == "hyperband") {
          n_evaluations <- 20  # base grid size
          opt_result <- tune_race_anova(
            wf, resamples = cv_folds, param_info = model_config$params,
            grid = 20, metrics = comprehensive_metrics,
            control = control_race(verbose = FALSE, save_workflow = FALSE)
          )
        }
        
        # Track evaluations
        for (i in 1:n_evaluations) {
          track_evaluation(experiment_id)
        }
        
      }, error = function(e) {
        cat("ERROR in optimization:", substr(e$message, 1, 80), "...\n")
        opt_result <- NULL
      })
      
      end_time <- Sys.time()
      training_time <- as.numeric(difftime(end_time, start_time, units = "mins"))
      
      # Calculate efficiency metrics
      efficiency_score <- ifelse(training_time > 0, n_evaluations / training_time, 0)
      time_per_evaluation <- ifelse(n_evaluations > 0, training_time / n_evaluations, 0)
      if (!is.null(opt_result) && opt_name != "genetic") {
        tryCatch({
          best_result <- select_best(opt_result, metric = "f_meas")
          best_params <- as.list(best_result[names(best_result) != ".config"])
          cv_metrics <- collect_metrics(opt_result) %>%
            filter(.config == best_result$.config)
        }, error = function(e) {
          cat("    ⚠ Error extracting CV results:", e$message, "\n")
          best_params <- NULL
          cv_metrics <- NULL
        })
      }

      # Run stability analysis for stochastic methods
      stability_metrics <- NULL
      if (opt_config$type == "Stochastic" && !is.null(best_params)) {
        cat("Running stability analysis...\n")
        stability_metrics <- run_stability_analysis(wf, cv_folds, model_config$params, opt_name)
      }
      
      # Test evaluation with comprehensive metrics
      test_metrics <- NULL
      if (!is.null(best_params) && !any(is.na(unlist(best_params)))) {
        tryCatch({
          # Fit final model
          final_wf <- finalize_workflow(wf, best_params)
          final_fit <- fit(final_wf, train_data)
          
          # Predictions
          test_pred_class <- predict(final_fit, test_data)
          test_pred_prob <- predict(final_fit, test_data, type = "prob")
          
          # Calculate comprehensive metrics
          test_results_df <- test_data %>%
            select(severe_maleria) %>%
            bind_cols(test_pred_class) %>%
            bind_cols(test_pred_prob)
          
          # Use manual calculation as backup
          manual_metrics <- calculate_comprehensive_metrics(
            truth = test_results_df$severe_maleria,
            estimate = test_results_df$.pred_class,
            prob_severe = test_results_df$.pred_Severe
          )
          
          test_metrics <- manual_metrics
          
        }, error = function(e) {
          cat("Error in test evaluation:", e$message, "\n")
          test_metrics <- NULL
        })
      }
      
      # Store results with enhanced metrics
      if (!is.null(best_params) && (!is.null(cv_metrics) || !is.null(test_metrics))) {
        
        # Extract CV metrics
        cv_f1 <- if (!is.null(cv_metrics)) {
          cv_f1_val <- cv_metrics %>% filter(.metric == "f_meas") %>% pull(mean)
          ifelse(length(cv_f1_val) > 0, cv_f1_val, NA)
        } else { NA }
        
        cv_accuracy <- if (!is.null(cv_metrics)) {
          cv_acc_val <- cv_metrics %>% filter(.metric == "accuracy") %>% pull(mean)
          ifelse(length(cv_acc_val) > 0, cv_acc_val, NA)
        } else { NA }
        
        cv_roc_auc <- if (!is.null(cv_metrics)) {
          cv_auc_val <- cv_metrics %>% filter(.metric == "roc_auc") %>% pull(mean)
          ifelse(length(cv_auc_val) > 0, cv_auc_val, NA)
        } else { NA }
        
        # Create comprehensive result row
        result_row <- data.frame(
          dataset = dataset_name,
          model = model_name,
          model_name = model_config$name,
          optimization_method = opt_config$name,
          optimization_type = opt_config$type,
          
          # Cross-validation metrics
          cv_f1_score = cv_f1,
          cv_accuracy = cv_accuracy,
          cv_roc_auc = cv_roc_auc,
          
          # Test metrics
          test_accuracy = ifelse(is.null(test_metrics), NA, test_metrics$accuracy),
          test_f1_score = ifelse(is.null(test_metrics), NA, test_metrics$f1_score),
          test_precision = ifelse(is.null(test_metrics), NA, test_metrics$precision),
          test_recall = ifelse(is.null(test_metrics), NA, test_metrics$recall),
          test_specificity = ifelse(is.null(test_metrics), NA, test_metrics$specificity),
          test_roc_auc = ifelse(is.null(test_metrics), NA, test_metrics$roc_auc),
          test_balanced_accuracy = ifelse(is.null(test_metrics), NA, test_metrics$balanced_accuracy),
          test_mcc = ifelse(is.null(test_metrics), NA, test_metrics$mcc),
          test_kappa = ifelse(is.null(test_metrics), NA, test_metrics$kappa),
          
          # Efficiency metrics
          training_time_minutes = training_time,
          n_evaluations = n_evaluations,
          efficiency_score = efficiency_score,
          time_per_evaluation = time_per_evaluation,
          
          # Stability metrics (for stochastic methods)
          stability_mean_f1 = ifelse(is.null(stability_metrics), NA, stability_metrics$mean_f1),
          stability_sd_f1 = ifelse(is.null(stability_metrics), NA, stability_metrics$sd_f1),
          stability_cv_f1 = ifelse(is.null(stability_metrics), NA, stability_metrics$cv_f1),
          stability_range_f1 = ifelse(is.null(stability_metrics), NA, 
                                     stability_metrics$max_f1 - stability_metrics$min_f1),
          n_successful_runs = ifelse(is.null(stability_metrics), NA, stability_metrics$n_successful_runs),
          
          stringsAsFactors = FALSE
        )
        
        all_results[[experiment_id]] <- result_row
        
        # Print summary
        cat("CV: F1=", round(cv_f1, 3), "ACC=", round(cv_accuracy, 3), "AUC=", round(cv_roc_auc, 3), "\n")
        if (!is.null(test_metrics)) {
          cat("Test: F1=", round(test_metrics$f1_score, 3), 
              "ACC=", round(test_metrics$accuracy, 3), 
              "AUC=", round(ifelse(is.na(test_metrics$roc_auc), 0, test_metrics$roc_auc), 3), "\n")
        }
        cat("Efficiency: ", n_evaluations, "evals in", round(training_time, 2), "min",
            "(", round(time_per_evaluation * 60, 1), "sec/eval)\n")
        
        if (!is.null(stability_metrics)) {
          cat("Stability: SD=", round(stability_metrics$sd_f1, 4), 
              "CV=", round(stability_metrics$cv_f1, 3), "\n")
        }
        
      } else {
        cat("failed - no valid results\n")
      }
    }
  }
  
  # Combine results
  if (length(all_results) > 0) {
    return(do.call(rbind, all_results))
  } else {
    return(data.frame())
  }
}
```

# Execute Comprehensive Analysis

```{r execute-comprehensive-analysis}
# Run comprehensive analysis on all datasets
final_results <- data.frame()
dataset_summaries <- list()

for (i in seq_along(all_datasets)) {
  dataset_name <- names(all_datasets)[i]
  dataset <- all_datasets[[i]]
  
  cat("\n", rep("=", 90), "\n")
  cat("Processing Dataset:", dataset_name, "\n")
  cat(rep("=", 90), "\n")
  
  results <- tryCatch({
    run_comprehensive_analysis(dataset, dataset_name)
  }, error = function(e) {
    cat("Error Processing", dataset_name, ":", e$message, "\n")
    data.frame()
  })
  
  if (nrow(results) > 0) {
    final_results <- rbind(final_results, results)
    cat("Successfully added", nrow(results), "results from", dataset_name, "\n")
    
    # Store dataset summary
    dataset_summaries[[dataset_name]] <- list(
      n_experiments = nrow(results),
      n_successful = sum(!is.na(results$test_f1_score)),
      best_f1 = max(results$test_f1_score, na.rm = TRUE),
      best_accuracy = max(results$test_accuracy, na.rm = TRUE)
    )
  } else {
    cat("No results obtained from", dataset_name, "\n")
  }
}

# Final Analysis Summary
cat("\n", rep("=", 90), "\n")
cat("Comprehensive Analysis Completed\n")
cat(rep("=", 90), "\n")

if (nrow(final_results) > 0) {
  cat("Overall Statistics\n")
  cat("Total experiments conducted:", nrow(final_results), "\n")
  cat("Successful experiments:", sum(!is.na(final_results$test_f1_score)), "\n")
  cat("Success rate:", round(100 * sum(!is.na(final_results$test_f1_score)) / nrow(final_results), 1), "%\n")
  
  valid_results <- final_results[!is.na(final_results$test_f1_score), ]
  
  if (nrow(valid_results) > 0) {
    cat("\nPerformance Highlights:\n")
    cat("Best F1-Score:", round(max(valid_results$test_f1_score), 4), "\n")
    cat("Best Accuracy:", round(max(valid_results$test_accuracy), 4), "\n")
    cat("Best ROC-AUC:", round(max(valid_results$test_roc_auc, na.rm = TRUE), 4), "\n")
    cat("Average F1-Score:", round(mean(valid_results$test_f1_score), 4), "\n")
    
    # Best performing combination
    best_idx <- which.max(valid_results$test_f1_score)
    best_combo <- valid_results[best_idx, ]
    
    cat("\n Best Performance Combination:\n")
    cat("Dataset:", best_combo$dataset, "\n")
    cat("Model:", best_combo$model_name, "\n")
    cat("Optimization:", best_combo$optimization_method, "\n")
    cat("F1-Score:", round(best_combo$test_f1_score, 4), "\n")
    cat("Accuracy:", round(best_combo$test_accuracy, 4), "\n")
    cat("ROC-AUC:", round(best_combo$test_roc_auc, 4), "\n")
  }
}
```

# Advanced Statistical Analysis

```{r advanced-statistical-analysis}
if (nrow(final_results) > 0 && sum(!is.na(final_results$test_f1_score)) > 0) {
  
  valid_results <- final_results[!is.na(final_results$test_f1_score), ]
  
  cat("\n", rep("=", 80), "\n")
  cat("Advanced Statistical Analysis\n")
  cat(rep("=", 80), "\n")
  
  # Deterministic vs Stochastic Comparison
  cat("\n Determinist vs StochasticN:\n")
  
  type_comparison <- valid_results %>%
    group_by(optimization_type) %>%
    summarise(
      n_experiments = n(),
      mean_f1 = mean(test_f1_score, na.rm = TRUE),
      sd_f1 = sd(test_f1_score, na.rm = TRUE),
      mean_accuracy = mean(test_accuracy, na.rm = TRUE),
      sd_accuracy = sd(test_accuracy, na.rm = TRUE),
      mean_roc_auc = mean(test_roc_auc, na.rm = TRUE),
      mean_time = mean(training_time_minutes, na.rm = TRUE),
      .groups = 'drop'
    ) %>%
    arrange(desc(mean_f1))
  
  print(type_comparison)
  
  # Statistical significance test
  det_results <- valid_results$test_f1_score[valid_results$optimization_type == "Deterministic"]
  sto_results <- valid_results$test_f1_score[valid_results$optimization_type == "Stochastic"]
  
  if (length(det_results) > 2 && length(sto_results) > 2) {
    tryCatch({
      t_test <- t.test(det_results, sto_results)
      wilcox_test <- wilcox.test(det_results, sto_results)
      
      cat("\nStatistical Tests\n")
      cat("Welch's t-test p-value:", round(t_test$p.value, 4), "\n")
      cat("Mann-Whitney U p-value:", round(wilcox_test$p.value, 4), "\n")
      cat("Significant difference (α=0.05):", 
          ifelse(min(t_test$p.value, wilcox_test$p.value) < 0.05, "YES", "NO"), "\n")
      
      if (mean(det_results) > mean(sto_results)) {
        cat("Deterministic methods outperform stochastic by", 
            round((mean(det_results) - mean(sto_results)) * 100, 2), "percentage points\n")
      } else {
        cat("Stochastic methods outperform deterministic by", 
            round((mean(sto_results) - mean(det_results)) * 100, 2), "percentage points\n")
      }
    }, error = function(e) {
      cat("Could not perform statistical tests\n")
    })
  }
  
  # Model Performance Analysis
  cat("\n Model Performance Ranking\n")
  
  model_performance <- valid_results %>%
    group_by(model_name) %>%
    summarise(
      n_experiments = n(),
      mean_f1 = mean(test_f1_score, na.rm = TRUE),
      sd_f1 = sd(test_f1_score, na.rm = TRUE),
      mean_accuracy = mean(test_accuracy, na.rm = TRUE),
      mean_precision = mean(test_precision, na.rm = TRUE),
      mean_recall = mean(test_recall, na.rm = TRUE),
      mean_roc_auc = mean(test_roc_auc, na.rm = TRUE),
      consistency = sd(test_f1_score, na.rm = TRUE) / mean(test_f1_score, na.rm = TRUE),
      .groups = 'drop'
    ) %>%
    arrange(desc(mean_f1))
  
  print(model_performance)
  
  # Optimization Method Analysis
  cat("\n Optimization Method Analysis:\n")
  
  method_performance <- valid_results %>%
    group_by(optimization_method, optimization_type) %>%
    summarise(
      n_experiments = n(),
      mean_f1 = mean(test_f1_score, na.rm = TRUE),
      sd_f1 = sd(test_f1_score, na.rm = TRUE),
      mean_accuracy = mean(test_accuracy, na.rm = TRUE),
      mean_time = mean(training_time_minutes, na.rm = TRUE),
      efficiency = mean(test_f1_score, na.rm = TRUE) / mean(training_time_minutes, na.rm = TRUE),
      .groups = 'drop'
    ) %>%
    arrange(desc(mean_f1))
  
  print(method_performance)
  
  # Dataset Complexity Analysis
  cat("\n Dataset Complexity Analysis:\n")
  
  dataset_performance <- valid_results %>%
    group_by(dataset) %>%
    summarise(
      n_experiments = n(),
      mean_f1 = mean(test_f1_score, na.rm = TRUE),
      sd_f1 = sd(test_f1_score, na.rm = TRUE),
      best_f1 = max(test_f1_score, na.rm = TRUE),
      worst_f1 = min(test_f1_score, na.rm = TRUE),
      range_f1 = max(test_f1_score, na.rm = TRUE) - min(test_f1_score, na.rm = TRUE),
      .groups = 'drop'
    ) %>%
    arrange(desc(mean_f1))
  
  print(dataset_performance)
  
  # Model-Method Interaction Analysis
  cat("\n Best Model-Method Interaction:\n")
  
  best_combinations <- valid_results %>%
    group_by(model_name, optimization_method) %>%
    summarise(
      mean_f1 = mean(test_f1_score, na.rm = TRUE),
      mean_accuracy = mean(test_accuracy, na.rm = TRUE),
      mean_time = mean(training_time_minutes, na.rm = TRUE),
      .groups = 'drop'
    ) %>%
    arrange(desc(mean_f1)) %>%
    head(10)
  
  print(best_combinations)
  
  # Efficiency Analysis
  cat("\n Efficiency Analysis:\n")
  
  efficiency_analysis <- valid_results %>%
    group_by(optimization_method, optimization_type) %>%
    summarise(
      mean_efficiency = mean(efficiency_score, na.rm = TRUE),
      mean_time_per_eval = mean(time_per_evaluation, na.rm = TRUE),
      mean_total_time = mean(training_time_minutes, na.rm = TRUE),
      mean_evaluations = mean(n_evaluations, na.rm = TRUE),
      .groups = 'drop'
    ) %>%
    arrange(desc(mean_efficiency))
  
  print(efficiency_analysis)
  
  # Stability Analysis for Stochastic Methods
  cat("\n Stability Analysis:\n")
  
  stability_results <- valid_results %>%
    filter(optimization_type == "Stochastic", !is.na(stability_cv_f1)) %>%
    group_by(optimization_method) %>%
    summarise(
      n_experiments = n(),
      mean_stability_cv = mean(stability_cv_f1, na.rm = TRUE),
      mean_stability_sd = mean(stability_sd_f1, na.rm = TRUE),
      mean_stability_range = mean(stability_range_f1, na.rm = TRUE),
      avg_successful_runs = mean(n_successful_runs, na.rm = TRUE),
      .groups = 'drop'
    ) %>%
    arrange(mean_stability_cv)
  
  if (nrow(stability_results) > 0) {
    print(stability_results)
  } else {
    cat("No stability data available for stochastic methods\n")
  }
}
```

# Comprehensive Visualizations

```{r comprehensive-visualizations}
if (nrow(final_results) > 0 && sum(!is.na(final_results$test_f1_score)) > 0) {
  
  valid_results <- final_results[!is.na(final_results$test_f1_score), ]
  
  # Load ggplot2 for visualizations
  library(ggplot2)
  library(patchwork)
  
  # Deterministic vs Stochastic Comparison
  p1 <- ggplot(valid_results, aes(x = optimization_type, y = test_f1_score, 
                                  fill = optimization_type)) +
    geom_violin(alpha = 0.7, width = 0.8) +
    geom_boxplot(width = 0.3, alpha = 0.8) +
    geom_jitter(width = 0.1, alpha = 0.5, size = 1.5) +
    theme_minimal() +
    theme(legend.position = "none") +
    labs(title = "F1-Score: Deterministic vs Stochastic Methods",
         x = "Optimization Type", y = "Test F1-Score") +
    scale_fill_manual(values = c("Deterministic" = "#2E86AB", "Stochastic" = "#A23B72"))
  
  # Model Performance Comparison
  p2 <- ggplot(valid_results, aes(x = reorder(model_name, test_f1_score), 
                                  y = test_f1_score, fill = model_name)) +
    geom_violin(alpha = 0.7) +
    geom_boxplot(width = 0.3, alpha = 0.8) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none") +
    labs(title = "Model Performance Comparison",
         x = "Model", y = "Test F1-Score")
  
  # Optimization Method Detailed Comparison
  p3 <- ggplot(valid_results, aes(x = reorder(optimization_method, test_f1_score), 
                                  y = test_f1_score, fill = optimization_type)) +
    geom_violin(alpha = 0.7) +
    geom_boxplot(width = 0.4, alpha = 0.8) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = "Optimization Method Performance",
         x = "Optimization Method", y = "Test F1-Score",
         fill = "Method Type") +
    scale_fill_manual(values = c("Deterministic" = "#2E86AB", "Stochastic" = "#A23B72"))
  
  # Performance vs Time Trade-off
  p4 <- ggplot(valid_results, aes(x = training_time_minutes, y = test_f1_score, 
                                  color = optimization_type, shape = model_name)) +
    geom_point(size = 2.5, alpha = 0.7) +
    geom_smooth(aes(group = optimization_type), method = "lm", se = FALSE) +
    theme_minimal() +
    labs(title = "Performance vs Training Time",
         x = "Training Time (minutes)", y = "Test F1-Score",
         color = "Optimization Type", shape = "Model") +
    scale_color_manual(values = c("Deterministic" = "#2E86AB", "Stochastic" = "#A23B72"))
  
  # Dataset Complexity Impact
  p5 <- ggplot(valid_results, aes(x = reorder(dataset, test_f1_score), 
                                  y = test_f1_score, fill = dataset)) +
    geom_violin(alpha = 0.7) +
    geom_boxplot(width = 0.3, alpha = 0.8) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none") +
    labs(title = "Performance by Dataset Complexity",
         x = "Dataset", y = "Test F1-Score")
  
  # 6. Multi-metric Comparison
  metrics_long <- valid_results %>%
    select(optimization_type, test_accuracy, test_f1_score, test_precision, 
           test_recall, test_specificity) %>%
    pivot_longer(cols = starts_with("test_"), 
                 names_to = "metric", 
                 values_to = "value") %>%
    mutate(metric = str_remove(metric, "test_")) %>%
    filter(!is.na(value))
  
  p6 <- ggplot(metrics_long, aes(x = metric, y = value, fill = optimization_type)) +
    geom_violin(alpha = 0.7, position = "dodge") +
    geom_boxplot(width = 0.2, alpha = 0.8, position = position_dodge(0.9)) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = "Multi-Metric Performance Comparison",
         x = "Metric", y = "Score", fill = "Optimization Type") +
    scale_fill_manual(values = c("Deterministic" = "#2E86AB", "Stochastic" = "#A23B72"))
  
  # Efficiency Analysis Plot
  p7 <- ggplot(valid_results, aes(x = efficiency_score, y = test_f1_score, 
                                  color = optimization_type, size = training_time_minutes)) +
    geom_point(alpha = 0.7) +
    theme_minimal() +
    labs(title = "Efficiency vs Performance Trade-off",
         x = "Efficiency Score (Evaluations/Minute)", y = "Test F1-Score",
         color = "Optimization Type", size = "Training Time (min)") +
    scale_color_manual(values = c("Deterministic" = "#2E86AB", "Stochastic" = "#A23B72"))
  
  # Stability Analysis Plot 
  stochastic_results <- valid_results %>% 
    filter(optimization_type == "Stochastic", !is.na(stability_cv_f1))
  
  if (nrow(stochastic_results) > 0) {
    p8 <- ggplot(stochastic_results, aes(x = stability_cv_f1, y = test_f1_score, 
                                         color = optimization_method)) +
      geom_point(size = 3, alpha = 0.7) +
      theme_minimal() +
      labs(title = "Stability vs Performance (Stochastic Methods)",
           x = "Coefficient of Variation (F1)", y = "Test F1-Score",
           color = "Method") +
      scale_x_reverse()  # Lower CV = better stability
  }
  
  # Combine plots
  combined_plot1 <- (p1 | p2) / (p3 | p4)
  combined_plot2 <- (p5 | p6) / (p7 | if(exists("p8")) p8 else plot_spacer())
  
  print(combined_plot1)
  print(combined_plot2)
  
  # Correlation Matrix of Metrics
  if (nrow(valid_results) > 5) {
    correlation_data <- valid_results %>%
      select(test_accuracy, test_f1_score, test_precision, test_recall, 
             test_specificity, test_roc_auc, training_time_minutes, 
             efficiency_score, n_evaluations) %>%
      cor(use = "complete.obs")
    
    # Convert to long format for ggplot
    cor_long <- correlation_data %>%
      as.data.frame() %>%
      rownames_to_column("var1") %>%
      pivot_longer(-var1, names_to = "var2", values_to = "correlation")
    
    p9 <- ggplot(cor_long, aes(x = var1, y = var2, fill = correlation)) +
      geom_tile() +
      geom_text(aes(label = round(correlation, 2)), size = 3) +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
      labs(title = "Correlation Matrix of Performance Metrics",
           x = "", y = "", fill = "Correlation") +
      scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0)
    
    print(p9)
  }
}
```

# Export Results and Final Summary

```{r export-comprehensive-results}
if (nrow(final_results) > 0) {
  
  # Export main results
  write_csv(final_results, "comprehensive_malaria_analysis_results.csv")
  cat("Main results exported to: comprehensive_malaria_analysis_results.csv\n")
  
  valid_results <- final_results[!is.na(final_results$test_f1_score), ]
  
  if (nrow(valid_results) > 0) {
    
    # Model Performance Summary
    model_summary <- valid_results %>%
      group_by(model_name) %>%
      summarise(
        experiments = n(),
        mean_f1 = round(mean(test_f1_score), 4),
        sd_f1 = round(sd(test_f1_score), 4),
        mean_accuracy = round(mean(test_accuracy), 4),
        mean_precision = round(mean(test_precision, na.rm = TRUE), 4),
        mean_recall = round(mean(test_recall, na.rm = TRUE), 4),
        mean_roc_auc = round(mean(test_roc_auc, na.rm = TRUE), 4),
        best_f1 = round(max(test_f1_score), 4),
        consistency_cv = round(sd(test_f1_score) / mean(test_f1_score), 3),
        mean_training_time = round(mean(training_time_minutes), 2),
        .groups = 'drop'
      ) %>%
      arrange(desc(mean_f1))
    
    write_csv(model_summary, "model_performance_comprehensive.csv")
    cat("Model summary exported to: model_performance_comprehensive.csv\n")
    
    # Optimization Method Summary
    method_summary <- valid_results %>%
      group_by(optimization_method, optimization_type) %>%
      summarise(
        experiments = n(),
        mean_f1 = round(mean(test_f1_score), 4),
        sd_f1 = round(sd(test_f1_score), 4),
        mean_accuracy = round(mean(test_accuracy), 4),
        mean_time_min = round(mean(training_time_minutes), 2),
        mean_efficiency = round(mean(efficiency_score, na.rm = TRUE), 4),
        mean_evaluations = round(mean(n_evaluations), 0),
        best_f1 = round(max(test_f1_score), 4),
        .groups = 'drop'
      ) %>%
      arrange(desc(mean_f1))
    
    write_csv(method_summary, "optimization_methods_comprehensive.csv")
    cat("Method summary exported to: optimization_methods_comprehensive.csv\n")
  
    # Dataset Analysis Summary
    dataset_summary <- valid_results %>%
      group_by(dataset) %>%
      summarise(
        experiments = n(),
        mean_f1 = round(mean(test_f1_score), 4),
        sd_f1 = round(sd(test_f1_score), 4),
        best_f1 = round(max(test_f1_score), 4),
        worst_f1 = round(min(test_f1_score), 4),
        range_f1 = round(max(test_f1_score) - min(test_f1_score), 4),
        mean_accuracy = round(mean(test_accuracy), 4),
        predictability = round(1 - (sd(test_f1_score) / mean(test_f1_score)), 3),
        mean_training_time = round(mean(training_time_minutes), 2),
        .groups = 'drop'
      ) %>%
      arrange(desc(mean_f1))
    
    write_csv(dataset_summary, "dataset_complexity_analysis.csv")
    cat("Dataset analysis exported to: dataset_complexity_analysis.csv\n")
    
    # Best Combinations
    best_combinations <- valid_results %>%
      group_by(dataset, model_name, optimization_method) %>%
      summarise(
        f1_score = max(test_f1_score),
        accuracy = test_accuracy[which.max(test_f1_score)],
        precision = test_precision[which.max(test_f1_score)],
        recall = test_recall[which.max(test_f1_score)],
        roc_auc = test_roc_auc[which.max(test_f1_score)],
        time_min = training_time_minutes[which.max(test_f1_score)],
        efficiency = efficiency_score[which.max(test_f1_score)],
        optimization_type = first(optimization_type),
        .groups = 'drop'
      ) %>%
      arrange(desc(f1_score)) %>%
      head(20)
    
    write_csv(best_combinations, "top_20_combinations.csv")
    cat("Top combinations exported to: top_20_combinations.csv\n")
    
    # Efficiency Analysis Summary
    efficiency_summary <- valid_results %>%
      group_by(optimization_method, optimization_type) %>%
      summarise(
        experiments = n(),
        mean_efficiency_score = round(mean(efficiency_score, na.rm = TRUE), 4),
        sd_efficiency_score = round(sd(efficiency_score, na.rm = TRUE), 4),
        mean_time_per_eval = round(mean(time_per_evaluation, na.rm = TRUE), 4),
        mean_total_evaluations = round(mean(n_evaluations), 0),
        mean_total_time = round(mean(training_time_minutes), 2),
        efficiency_rank = rank(-mean(efficiency_score, na.rm = TRUE)),
        .groups = 'drop'
      ) %>%
      arrange(desc(mean_efficiency_score))
    
    write_csv(efficiency_summary, "efficiency_analysis.csv")
    cat("Efficiency analysis exported to: efficiency_analysis.csv\n")
    
    # Statistical Analysis Summary
    det_results <- valid_results$test_f1_score[valid_results$optimization_type == "Deterministic"]
    sto_results <- valid_results$test_f1_score[valid_results$optimization_type == "Stochastic"]
    
    if (length(det_results) > 2 && length(sto_results) > 2) {
      stat_summary <- data.frame(
        deterministic_mean = round(mean(det_results), 4),
        deterministic_sd = round(sd(det_results), 4),
        deterministic_n = length(det_results),
        stochastic_mean = round(mean(sto_results), 4),
        stochastic_sd = round(sd(sto_results), 4),
        stochastic_n = length(sto_results),
        difference = round(mean(det_results) - mean(sto_results), 4),
        effect_size_cohens_d = round((mean(det_results) - mean(sto_results)) / 
                                   sqrt(((length(det_results)-1)*var(det_results) + 
                                        (length(sto_results)-1)*var(sto_results)) / 
                                        (length(det_results) + length(sto_results) - 2)), 4),
        t_test_pvalue = tryCatch(round(t.test(det_results, sto_results)$p.value, 6), 
                               error = function(e) NA),
        wilcox_test_pvalue = tryCatch(round(wilcox.test(det_results, sto_results)$p.value, 6), 
                                    error = function(e) NA)
      )
      
      write_csv(stat_summary, "statistical_comparison_summary.csv")
      cat("Statistical summary exported to: statistical_comparison_summary.csv\n")
    }
    
    # Stability Analysis Summary
    stability_data <- valid_results %>%
      filter(optimization_type == "Stochastic", !is.na(stability_cv_f1))
    
    if (nrow(stability_data) > 0) {
      stability_summary <- stability_data %>%
        group_by(optimization_method) %>%
        summarise(
          experiments = n(),
          mean_stability_cv = round(mean(stability_cv_f1, na.rm = TRUE), 4),
          sd_stability_cv = round(sd(stability_cv_f1, na.rm = TRUE), 4),
          mean_stability_sd = round(mean(stability_sd_f1, na.rm = TRUE), 4),
          mean_stability_range = round(mean(stability_range_f1, na.rm = TRUE), 4),
          avg_successful_runs = round(mean(n_successful_runs, na.rm = TRUE), 1),
          most_stable = rank(mean(stability_cv_f1, na.rm = TRUE)),
          .groups = 'drop'
        ) %>%
        arrange(mean_stability_cv)
      
      write_csv(stability_summary, "stability_analysis_stochastic.csv")
      cat("Stability analysis exported to: stability_analysis_stochastic.csv\n")
    }
  }
  
  # Final Summary Report
  cat("\n", rep("=", 90), "\n")
  cat("Comprehensive Analysis Complete\n")
  cat(rep("=", 90), "\n")
  
  cat("Files Created:\n")
  files_created <- c("comprehensive_malaria_analysis_results.csv",
                     "model_performance_comprehensive.csv", 
                     "optimization_methods_comprehensive.csv",
                     "dataset_complexity_analysis.csv",
                     "top_20_combinations.csv",
                     "efficiency_analysis.csv",
                     "statistical_comparison_summary.csv",
                     "stability_analysis_stochastic.csv")
  
  for (file in files_created) {
    if (file.exists(file)) {
      size_kb <- round(file.size(file) / 1024, 1)
      cat(file, "(", size_kb, "KB)\n")
    }
  }
  
  if (nrow(valid_results) > 0) {
    cat("\n Key Findings:\n")
    
    # Overall best
    best_overall <- valid_results[which.max(valid_results$test_f1_score), ]
    cat("Overall Best F1-Score:", round(best_overall$test_f1_score, 4), "\n")
    cat("Model:", best_overall$model_name, "\n")
    cat("Method:", best_overall$optimization_method, "\n")
    cat("Dataset:", best_overall$dataset, "\n")
    cat("Training Time:", round(best_overall$training_time_minutes, 2), "minutes\n")
    
    # Type comparison
    type_comp <- valid_results %>%
      group_by(optimization_type) %>%
      summarise(
        mean_f1 = mean(test_f1_score),
        mean_efficiency = mean(efficiency_score, na.rm = TRUE),
        mean_time = mean(training_time_minutes),
        .groups = 'drop'
      )
    
    if (nrow(type_comp) == 2) {
      winner <- type_comp$optimization_type[which.max(type_comp$mean_f1)]
      difference <- max(type_comp$mean_f1) - min(type_comp$mean_f1)
      cat("Winner (Performance):", winner, "methods\n")
      cat("Performance advantage:", round(difference * 100, 2), "percentage points\n")
      
      efficiency_winner <- type_comp$optimization_type[which.max(type_comp$mean_efficiency)]
      cat("Winner (Efficiency):", efficiency_winner, "methods\n")
    }
    
    # Best model
    best_model <- valid_results %>% 
      group_by(model_name) %>% 
      summarise(mean_f1 = mean(test_f1_score), .groups = 'drop') %>%
      slice_max(mean_f1, n = 1)
    cat("Best Model Overall:", best_model$model_name, 
        "(F1:", round(best_model$mean_f1, 4), ")\n")
    
    # Best method
    best_method <- valid_results %>% 
      group_by(optimization_method) %>% 
      summarise(mean_f1 = mean(test_f1_score), .groups = 'drop') %>%
      slice_max(mean_f1, n = 1)
    cat("Best Optimization Method:", best_method$optimization_method,
        "(F1:", round(best_method$mean_f1, 4), ")\n")
    
    # Most efficient method
    most_efficient <- valid_results %>% 
      group_by(optimization_method) %>% 
      summarise(mean_efficiency = mean(efficiency_score, na.rm = TRUE), .groups = 'drop') %>%
      slice_max(mean_efficiency, n = 1)
    cat("Most Efficient Method:", most_efficient$optimization_method,
        "(", round(most_efficient$mean_efficiency, 2), "evals/min)\n")
    
    # Cross-validation improvement
    cv_improvement <- valid_results %>%
      summarise(
        mean_cv_f1 = mean(cv_f1_score, na.rm = TRUE),
        mean_test_f1 = mean(test_f1_score, na.rm = TRUE)
      )
    
    if (!is.na(cv_improvement$mean_cv_f1) && !is.na(cv_improvement$mean_test_f1)) {
      generalization_gap <- cv_improvement$mean_cv_f1 - cv_improvement$mean_test_f1
      cat("Generalization Gap (CV - Test):", round(generalization_gap, 4), "\n")
      if (generalization_gap > 0.02) {
        cat("Potential overfitting detected\n")
      } else if (generalization_gap < -0.02) {
        cat("Models generalize well to unseen data\n")
      } else {
        cat("Good generalization performance\n")
      }
    }
  }
  
} else {
  cat("No valid results to export\n")
}

cat("\n Analysis completed successfully!\n")
```

# Session Information and Reproducibility

```{r session-info}
cat("\n", rep("=", 80), "\n")
cat("Session Information\n")
cat(rep("=", 80), "\n")

# R session info
cat("R Version:", R.version.string, "\n")
cat("Date:", Sys.Date(), "\n")
cat("Time:", format(Sys.time(), "%H:%M:%S"), "\n")

# Package versions
cat("\n Key Package Version\n")
key_packages <- c("tidyverse", "tidymodels", "xgboost", "ranger", 
                  "kernlab", "glmnet", "nnet", "kknn")

for (pkg in key_packages) {
  if (requireNamespace(pkg, quietly = TRUE)) {
    version <- packageVersion(pkg)
    cat(pkg, ":", as.character(version), "\n")
  }
}

# System info
cat("\n System Information:\n")
cat("Platform:", Sys.info()["sysname"], "\n")
cat("Machine:", Sys.info()["machine"], "\n")
cat("CPU Cores:", parallel::detectCores(), "\n")

# Reproducibility info
cat("\n Reproducibility:\n")
cat("Global seed: 123\n")
cat("Cross-validation: 10-fold repeated 5 times\n")
cat("Data split: 75% train / 25% test (stratified)\n")

cat("\nAnalysis completed successfully!")
cat("\nAll results have been exported to CSV files for further analysis.")
```
